\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\newcommand{\R}{\mathbb{R}}

\title{Algorithmic Operation Research \\ Homework 4}
\date{8-11-2019}
\author{Theodora Panagea - 1115201400135 \\ Anna-Aikaterini Kavvada - 1115201500050}

\begin{document}
	\maketitle{}
  	\pagenumbering{arabic}
  	
%-------------------Exercise 1--------------------------

\subsection*{Exercise 1}
\textit{Consider the problem 
$$\text{minimize \qquad} 2x_1 + 3 \vert x_2 - 10 \vert$$
$$\text{subject to \quad} \vert x_1 + 2 \vert + \vert x_2 \vert \leqslant 5 $$
and reformulate it a linear programming problem. 
}
\\
\textbf{Solution:} \\
Our \textbf{goal} is to replace the absolute values with a variable $y_i$. The absolute values can be written as: \\
$$  \vert x_2 - 10 \vert = \max{\lbrace-x_2+10, x_2-10\rbrace} = y_1$$ 
$$ \vert x_1 + 2 \vert  = \max{\lbrace-x_1 + 2, - x_1 - 2 \rbrace} = y_2$$
$$\vert x_2 \vert = \max{\lbrace x_2, -x_2 \rbrace} = y_3$$ 
Furthermore, we also have to add some constraints for the absolute values that we replaced:
\begin{align*}
y_1 &\geqslant x_2 - 10  \\
y_1 &\geqslant -x_2 + 10 \\
\end{align*}
In that case, the minimum possible value of $y_1$ is $ \vert x_2 - 10 \vert$. Similarily, for $y_2, y_3$: \\
\begin{align*}
y_2 &\geqslant x_1 + 2 \\
y_2 &\geqslant -x_1 - 2 \\
y_3 &\geqslant x_2 \\
y_3 &\geqslant -x_2
\end{align*}
To conclude, the problem reformulates as follows: 
\begin{align*}
\text{minimize \quad} 2x_1 &+ 3y_1 \\
\text{subject to \quad} y_2 &+ y_3 \leqslant 5 \\
y_1 &\geqslant x_2 - 10  \\
y_1 &\geqslant -x_2 + 10 \\
y_2 &\geqslant x_1 + 2 \\
y_2 &\geqslant -x_1 - 2 \\
y_3 &\geqslant x_2 \\
y_3 &\geqslant -x_2
\end{align*}
\newpage

%-------------------Exercise 2--------------------------

\subsection*{Exercise 2}
\textit{(Road Lighting) Consider a road divided in $n$ segments that is illuminated by $m$ lamps. Let $p_j$ be the power of the j-th lamp. The illumination $I_i$ of the i-th segment is assumed to be $\sum_{j=1}^m{a_{ij}p_{j}}$ where $a_{ij}$ are known coefficients. Let $I_i^{*}$ be the desired illumination of road $i$. We are interested in choosing the lamp powers $p_j$ so that the illuminations $I_i$ are close to the desired $I_i^{*}$. Provide a reasonable linear programming formulation of this problem.} \\
\textbf{Solution:} \\
Our \textbf{goal} is to minimize the difference between the desired (optimal) value and $I_i^{*}$ and the current illumination $I_i$ the segment $i$ of the road has. \\
Thus, we ask in a mathematical form, for: 
$$\text{minimize} \sum_{i=1}^n{\vert I_i^{*} - I_i \vert}$$
where $I_i = \sum_{j=1}^m{a_{ij}p_{j}}$ . So the cost function can be written as: 
$$\text{minimize} \sum_{i=1}^n{\vert I_i^{*} - \sum_{j=1}^m{a_{ij}p_{j}} \vert}$$
From the above function, knowing that $a_{ij}$ being coefficients, we conclude that $p_j$ is our variable of the equation. That leads us to the following constraint: $$p_j \geqslant 0 $$
In conclusion, we end up with the following linear programming formulation: 
$$ \text{  minimize \quad} \quad \sum_{i=1}^n{\vert I_i^{*} - I_i \vert}$$
$$ \text{subject to \quad} \quad  p_j \geqslant 0 $$
\newpage

%-------------------Exercise 3--------------------------

\subsection*{Exercise 3}
\textit{Consider a school district with with $I$ neighborhoods, $J$ schools and $G$ grades at each school. Each school $j$ has capacity $C_jg$ for grade $g$. In each neighborhood $i$, the student population of grade $i$ is $S_{ig}$. Finally, the distance of school $j$ from neighborhood $i$ is $d_{ij}$. Formulate a linear programming problem whose objective is to assign all students to schools, while minimizing the total distance traveled by all students. (You may ignore the fact that numbers of students must be integer).} \newline
\textbf{Solution:} \\
Suppose $x_{ijg}$ students from neighborhood $i$ going to school $j$ and being in $g$ grade. \par
\textbf{Goal:} minimize the distance that the students have to travel, thus we want the min sum of the distance each student has to travel. 
\begin{equation}
\text{minimize} \qquad \sum_{i \in I} \sum_{j \in J} \sum_{g \in G} x_{ijg}d_{ij} 
\end{equation} \par 
\textbf{Restrictions:}
\begin{itemize}
\item All students from a neighborhood $i$ being on grade $g$ must get in a school.
	\begin{equation}
	S_{ig} = \sum_{j \in J} x_{ijg} \qquad \forall g \in G \text{ and } i \in I	
	\end{equation}
\item Each school can take only $C_{jg}$ student for every grade. 
	\begin{equation}
		\sum_{i \in I} x_{ijg} \leqslant C_{jg} \qquad \forall j \in J \text{ and } g \in G	
	\end{equation}
\item We can't have negative numbers. 
	\begin{equation}
		x \geqslant 0
	\end{equation}
\end{itemize}
Thus, we conclude to the following linear programming formulation: 
\begin{align*}
\text{minimize } &\sum_{i \in I} \sum_{j \in J} \sum_{g \in G} x_{ijg}d_{ij} \\
\text{subject to } &\sum_{j \in J} x_{ijg} = S_{ig}  \qquad \forall g \in G \text{ and } i \in I \\
&\sum_{i \in I} x_{ijg} \leqslant C_{jg} \qquad \forall j \in J \text{ and } g \in G \\
&x \geqslant 0
\end{align*}

\newpage
%-------------------Exercise 4--------------------------

\subsection*{Exercise 4}
\textit{Consider a set $P$ described by linear inequality constraints 
$$P = \lbrace x \in \R^n : a_i^{\prime}x  \leqslant b_i, i = 1, \ldots, m \rbrace$$
A ball with center $y$ and radius $r$ is defined as all the set of all points within distance $r$ from $y$. We are interested in finding a ball with the largest possible radius, which is entirely contained within the set $P$. Provide a linear programming formulation of this problem. } \\
\textbf{Solution:}
The optimal solution is to examine a point on the boundary of P. \\
So, we want to maximize the shortest distance (i.e. the line segment) between $y$ and the boundary point. \\
If we take the product of $y$ and the vector $a_i^{\prime}$, then the distance and therefore, the problem would be: 
	\begin{align*}
		\text{minimize }  \qquad   &\text{max}_i{\lbrace -\vert a_i^{\prime}y - b_i \vert \rbrace} 	\\
		\text{subject to }  \qquad &a_i^{\prime}y \leqslant b_i, \qquad &i = 1, \ldots, m
	\end{align*}

\end{document}  